---
title: "Jawbone Data: 2016 - 2017"
output: html_notebook
---


```{r}
data = read.csv("JawboneData/2016_jwbn.csv", header = TRUE)
d = read.csv("JawboneData/2017_jwbn.csv", header = TRUE)

# colnames(data)
# colnames(d)

data = data[, -c(6:32)]
d = d[, -c(37:38)]

colnames(data)
colnames(d)

data = rbind(data, d)
rm(d)
```

```{r}
library(lubridate)
library(magrittr)

data$DATE = ymd(data$DATE)
data = data %>% 
  subset(DATE > as.Date("2016-05-21", "%Y-%m-%d") ) %>%
  subset(DATE <= as.Date("2017-09-02", "%Y-%m-%d") )
  

# Remove data with the most NA
x = as.data.frame(apply(data, 2, function(x) length(which(is.na(x)))) )
colnames(x)[1] = "numNA"
x = cbind(row.names(x),
          x)
colnames(x)[1] = "var"

library(dplyr)
x = arrange(x, desc(numNA))
x

# noquote(paste(x$var[1:15], collapse=", " ) ) 

data = data %>% subset(select = -c(body_fat, goal_body_weight, n_asleep_time, n_awake, n_awake_time, n_awakenings, n_bedtime, n_clinical_deep, n_count, n_deep, n_duration, n_light, n_quality, n_rem, n_to_bed_phr)) 

# Check NA
x = as.data.frame(apply(data, 2, function(x) length(which(is.na(x)))) )
colnames(x)[1] = "numNA"
x = cbind(row.names(x),
          x)
colnames(x)[1] = "var"
x
```

```{r}
# More date variables 
library(lubridate)
library(plyr)

data$month = month(data$DATE)
data$weekday = weekdays(data$DATE)
data$season = mapvalues(data$month,
                         from = c(12, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11),
                         to = c( "Winter", "Winter", "Winter",
                                "Spring", "Spring", "Spring",
                                "Summer",  "Summer", "Summer",
                                "Fall", "Fall", "Fall"))
data$is_weekend = mapvalues(data$weekday,
                             from = c("Friday", "Monday", 
                                      "Wednesday", "Thursday", 
                                      "Tuesday", 
                                      "Saturday", "Sunday"),
                             to = c( 0, 0,
                                     0, 0,
                                     0,
                                     1, 1))
data$is_weekend = as.numeric(data$is_weekend)

library(dummies)
wkdyD = as.data.frame(dummy(data$weekday))
data = cbind(wkdyD, data)
colnames(data)[1:7] = gsub(")", "", colnames(data)[1:7])
data[, 1] = NULL

seasD = as.data.frame(dummy(data$season))
data = cbind(seasD, data)
colnames(data)[1:4] = gsub(")", "", colnames(data)[1:4])
data[, 1] = NULL


mnthD = as.data.frame(dummy(data$month))
data = cbind(mnthD, data)
colnames(data)[1:12] = gsub(")", "", colnames(data)[1:12])
data[, 1] = NULL

# Remove duplicates of encoded variables
data$month = NULL
data$weekday = NULL
data$season = NULL

# Review variables 
str(data)
```



```{r}
# We use the multiplot function, courtesy of R Cookbooks to create multi-panel plots.
#
# Define multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot = function(..., plotlist=NULL, file, cols=1, layout=NULL) {

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


```{r}
library(ggplot2)
library(magrittr)
library(grid)

options(scipen = 999)
# Variable of interest
data %>%
  ggplot(aes(s_rem)) +
  geom_histogram(fill = "red", bins = 150)

p1 = data %>% ggplot(aes( x = s_clinical_deep)) +
  geom_bar() +
  theme(legend.position = "none") +
  labs(title = "Histogram: Deep Sleep Length",
       x = "s_clinical_deep",
       y = "Frequency")


p2 = data %>% ggplot(aes( x = rhr)) +
  geom_bar() +
  labs(title = "Histogram: RHR",
       x = "RHR",
       y = "Frequency") 

layout = matrix(c(1,2),1,2,byrow=TRUE)
multiplot(p1, p2, layout=layout)
```

```{r}
data
```

```{r}
data$gender = NULL
data$age = NULL
data$goal_body_weight_intent = NULL
data$height = NULL
data$s_count = NULL
data$s_deep = NULL
data$s_quality = NULL
data$weight = NULL


data
```

```{r}
library(caret)
set.seed(107)

# Removes 4 rows
data= na.omit(data)

inTrain = createDataPartition(y = data$s_rem, 
                               p = .80, 
                               list = FALSE)
train = data[ inTrain,]
test = data[-inTrain,]


filt_train = subset(train, select = c( DATE,
                                    s_duration,
                                    s_awake_time) )
train =  subset(train, select = -c( DATE,
                                    s_duration,
                                    s_awake_time) )

filt_test = subset(test, select = c( DATE,
                                    s_duration,
                                    s_awake_time) )
test =  subset(test, select = -c( DATE,
                                    s_duration,
                                    s_awake_time) )



mdl = train(x = subset(train, select = -c(s_rem) ),
            y = train$s_rem,
            method = "xgbTree",
            trControl = trainControl(method = "cv",
                                     number = 5))

mdl
varImp(mdl)

mdl2 = train(x = subset(train, select = -c(s_rem) ),
            y = train$s_rem,
            method = "bayesglm",
            trControl = trainControl(method = "cv",
                                     number = 5))
varImp(mdl2)

```


```{r}
## Metrics: Predictions
rmse = function(actual, pred)
{
    sqrt(mean((actual - pred)^2))
}

mae = function(actual, pred)
{
    mean(abs(actual - pred))
}
```


```{r}

## Different variable importances from the different models above - may benefit from ensemble modeling

# Predictions from test
pred_mdl = predict(mdl, subset(test, select = -c(s_rem)) )
pred_mdl2 = predict(mdl2, subset(test, select = -c(s_rem)) )

print("XGBoost Tree")
rmse(test$s_rem, pred_mdl )
mae(test$s_rem, pred_mdl)


print("Bayesian Generalized Linear Models")
rmse(test$s_rem, pred_mdl2 )
mae(test$s_rem, pred_mdl2)


library(caretEnsemble)

model_list = caretList(
  s_rem~., 
  data=train,
  trControl=trainControl(method = "cv", number = 5),
  methodList=c("bayesglm", "xgbTree")
  )

xyplot(resamples(model_list))
modelCor(resamples(model_list)) # Fairly uncorrelated & fairly similar accuracy as noted from metrics

```


```{r}
greedy_ensemble = caretEnsemble(
  model_list, 
  metric="RMSE",
  trControl=trainControl(method = "cv", number = 5) )
summary(greedy_ensemble)

# Get metrics for test
pred_mdl3 = predict(greedy_ensemble, 
                    subset(test, select = -c(s_rem)) )

print("Greedy Ensemble")
rmse(test$s_rem, pred_mdl3 )
mae(test$s_rem, pred_mdl3)

```

```{r}
imp = as.data.frame(varImp(greedy_ensemble) )
imp = cbind(imp, row.names(imp))
colnames(imp) = c("overall", "bayesglm", "xgbTree", "var")
library(plyr)
imp =arrange(imp ,desc(overall) )
imp

```

The ensemble model showed improved error metrics over the individual models. 
An examination of the overall variable importance points out that the resting heart rate,
deep sleep length, light sleep, awake, winter, the weekend, which makes sense since these factors can impact quality of rem sleep.

Of course, parameter tuning and other kinds of models can improve predictions.







